\documentclass[a4paper,12pt]{report}

% Basic packages for LuaLaTeX with Unicode support
\usepackage{fontspec}
\usepackage[brazil]{babel}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{indentfirst}
\usepackage{setspace}

% Hyperref configuration for better PDF output
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
    citecolor=green,
    pdftitle={Task 09: Install Exception Handler},
    pdfauthor={Your Name},
    pdfsubject={Memory Management in x86},
    pdfkeywords={exception handler, IDT, page fault, x86}
}

% Code listing styling
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=2
}

\lstset{style=mystyle}

\geometry{margin=2.5cm}
\onehalfspacing

\begin{document}

\chapter{Task 09: Install Exception Handler}

\section{Task Description}
The goal of this task is to install a page fault exception handler using the \texttt{init\_idt()} function. This involves setting up the Interrupt Descriptor Table (IDT) to handle page faults and ensuring the system can gracefully manage such exceptions.

\section{Planned Implementation}
\begin{enumerate}
    \item \textbf{Include Necessary Headers}:
    Ensure the \texttt{helper.h} file is included for access to the \texttt{init\_idt()} function and related utilities.

    \item \textbf{Initialize the IDT}:
    Call the \texttt{init\_idt()} function to set up the IDT and install the page fault handler.

    \item \textbf{Test the Handler}:
    Trigger a page fault by accessing an unmapped memory address. Verify that the handler is invoked and logs the appropriate message.

    \item \textbf{Log Results}:
    Ensure the handler outputs a message indicating a page fault has occurred.
\end{enumerate}

\section{Expected Outcome}
\begin{itemize}
    \item The IDT is successfully initialized with a page fault handler.
    \item Accessing unmapped memory triggers the handler.
    \item The handler logs a message such as \texttt{"Page fault"} to indicate the exception.
\end{itemize}

\section{Implementation Details}
(To be filled after implementation)

\section{Challenges}
(To be filled after implementation)

\section{Final Outcome}
(To be filled after implementation)

\end{document}
