\documentclass[a4paper,12pt]{report}

% Basic packages for LuaLaTeX with Unicode support
\usepackage{fontspec}
\usepackage[brazil]{babel}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{indentfirst}
\usepackage{setspace}

% Hyperref configuration
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
    pdftitle={Task 01: Enable Paging},
    pdfauthor={Your Name},
    pdfsubject={Memory Management in x86},
    pdfkeywords={paging, memory management, x86 architecture}
}

% Code listing styling
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=2
}

\lstset{style=mystyle}

\geometry{margin=2.5cm}
\onehalfspacing

\begin{document}

\chapter{Task 01: Enable Paging}

\section{Task Description}
Set up paging by initializing control registers and mapping the first 4MB of memory. This involves configuring the page table and enabling paging in the CPU.

\section{Planned Implementation}
\begin{enumerate}
    \item Declare the root page table aligned to 4096 bytes using the \texttt{\_\_attribute\_\_((aligned(4096)))} directive.
    \item Initialize the first 4MB with identity mapping using the value \texttt{(1 << 7) | (1 << 1) | (1 << 0)}:
    \begin{itemize}
        \item Bit 7: 4MB page.
        \item Bit 1: Read/Write.
        \item Bit 0: Present.
    \end{itemize}
    \item Set the \texttt{cr3} register to point to the root page table using the \texttt{set\_cr3()} function.
    \item Enable 4MB pages by setting bit 4 of \texttt{cr4} using \texttt{set\_cr4()} and \texttt{get\_cr4()}.
    \item Enable paging by setting bit 31 of \texttt{cr0} using \texttt{set\_cr0()} and \texttt{get\_cr0()}.
    \item Print \texttt{"Paginação habilitada"} to confirm that paging is enabled.
\end{enumerate}

\section{Expected Outcome}
\begin{itemize}
    \item The system successfully enables paging with the first 4MB of memory mapped.
    \item The message \texttt{"Paginação habilitada"} is displayed.
\end{itemize}

\section{Implementation Details}
(To be filled after implementation)

\section{Challenges}
(To be filled after implementation)

\section{Final Outcome}
(To be filled after implementation)

\end{document}
