\begin{abstract}
\selectlanguage{american}
This work presents the implementation of a system for detecting deadlocks and lock acquisition order violations, inspired by the Linux kernel's lockdep. The system monitors mutex operations in multithreaded programs, building a dependency graph between locks and detecting potential deadlock situations before they occur. We use two complementary approaches: (1) cycle detection in the dependency graph, which indicates a potential deadlock, and (2) verification of consistency in the order of lock acquisition across different threads. The system was implemented using two distinct techniques: a shared library that uses function interposition to intercept calls to the pthread API, and a ptrace-based tool capable of analyzing running processes, including those already in a deadlock state. Both implementations share a modular graph analysis library. Tests performed demonstrate the effectiveness of the system in detecting classic deadlocks such as the AB-BA problem, where two threads try to acquire the same mutexes in different orders, with each approach offering specific advantages for different scenarios. This work contributes to the development of tools that increase the robustness of concurrent systems, helping programmers identify synchronization problems that are difficult to detect.

\vspace{0.5cm}

\noindent\textbf{Keywords:} deadlock, mutex, concurrency, error detection, dependency graph, operating systems, ptrace, function interposition.
\selectlanguage{brazil}
\end{abstract}
