
\begin{thebibliography}{12}
\bibitem{linux}
    Rusty Russell,
    \emph{Unreliable Guide To Locking},
    Linux Kernel Docs > Kernel Hacking Guides > Unreliable Guide To Locking, 2018,
    \url{https://www.kernel.org/doc/html/v4.13/kernel-hacking/locking.html}.

\bibitem{lockdep}
  Rusty Russell,
  \emph{Lockdep: How to read its reports},
  Linux Kernel Documentation, 2006,
  \url{https://www.kernel.org/doc/html/latest/locking/lockdep-design.html}.

\bibitem{pthread}
  IEEE Computer Society,
  \emph{POSIX Thread Libraries},
  IEEE Std 1003.1-2017,
  \url{https://pubs.opengroup.org/onlinepubs/9699919799/basedefs/pthread.h.html}, 2017.

\bibitem{corbet}
  Jonathan Corbet,
  \emph{The kernel lock validator},
  \url{https://lwn.net/Articles/185666/},
  LWN.net, May 2006.

\bibitem{deadlock}
  Coffman, E.G., Elphick, M.J., Shoshani, A.,
  \emph{System Deadlocks},
  ACM Computing Surveys, Vol. 3, No. 2, pp. 67-78,
  \url{https://doi.org/10.1145/356586.356588}, 1971.

\bibitem{ptrace}
  Linux Manual Pages,
  \emph{ptrace(2) - process trace},
  \url{https://man7.org/linux/man-pages/man2/ptrace.2.html}, 2021.

\bibitem{futex}
  Hubertus Franke, Rusty Russell, Matthew Kirkwood,
  \emph{Futexes are Tricky},
  \url{https://www.kernel.org/doc/Documentation/locking/futex-requeue-pi.rst}, 2014.

\bibitem{backtrace}
  GNU Project,
  \emph{The GNU C Library: Backtraces},
  \url{https://www.gnu.org/software/libc/manual/html_node/Backtraces.html}, 2022.

\bibitem{valgrind}
  Nicholas Nethercote and Julian Seward,
  \emph{Valgrind: A Framework for Heavyweight Dynamic Binary Instrumentation},
  Proceedings of the 28th ACM SIGPLAN Conference on Programming Language Design and Implementation,
  \url{https://doi.org/10.1145/1250734.1250746}, PLDI 2007.

\bibitem{gdb}
  Free Software Foundation,
  \emph{Debugging with GDB},
  \url{https://sourceware.org/gdb/current/onlinedocs/gdb/}, 2023.

\bibitem{havender}
  Havender, J. W.,
  \emph{Avoiding deadlock in multitasking systems},
  IBM Systems Journal, Vol. 7, No. 2, pp. 74-84,
  \url{https://doi.org/10.1147/sj.72.0074}, 1968.

\bibitem{isloor}
  Isloor, S. S., and Marsland, T. A.,
  \emph{The Deadlock Problem: An Overview},
  IEEE Computer, Vol. 13, No. 9, pp. 58-78,
  \url{https://doi.org/10.1109/MC.1980.1653786}, September 1980.

\bibitem{singhal}
  Singhal, M.,
  \emph{Deadlock Detection in Distributed Systems},
  IEEE Computer, Vol. 22, No. 11, pp. 37-48,
  \url{https://doi.org/10.1109/2.43525}, November 1989.

\bibitem{knapp}
  Knapp, E.,
  \emph{Deadlock Detection in Distributed Databases},
  ACM Computing Surveys, Vol. 19, No. 4, pp. 303-328,
  \url{https://doi.org/10.1145/45075.46163}, 1987.

\bibitem{savage}
  Savage, S., Burrows, M., Nelson, G., Sobalvarro, P., Anderson, T.,
  \emph{Eraser: A Dynamic Data Race Detector for Multithreaded Programs},
  ACM Transactions on Computer Systems, Vol. 15, No. 4, pp. 391-411,
  \url{https://doi.org/10.1145/265924.265927}, 1997.

\bibitem{silberschatz}
  Silberschatz, A., Galvin, P. B., Gagne, G.,
  \emph{Operating System Concepts},
  9th Edition, John Wiley \& Sons,
  \url{http://os-book.com}, 2012.

\bibitem{levine}
  Levine, G. N.,
  \emph{Finding Deadlocks in Large Systems},
  PhD Thesis, University of Wisconsin-Madison,
  \url{https://minds.wisconsin.edu/handle/1793/7563}, 2003.

\bibitem{avd}
  Agarwal, R., Wang, L., Stoller, S.D.,
  \emph{Detecting Potential Deadlocks with Static Analysis and Run-Time Monitoring},
  Haifa Verification Conference, Springer, pp. 191-207,
  \url{https://link.springer.com/chapter/10.1007/11678779_14}, 2005.
\end{thebibliography}
% % \include{x_referencias/x01_referencias}
