\documentclass[a4paper,12pt]{report}

% Basic packages for LuaLaTeX with Unicode support
\usepackage{fontspec}
\usepackage[brazil]{babel}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{indentfirst}
\usepackage{setspace}

% Hyperref configuration
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
    pdftitle={Task 02: Test Paging Activation},
    pdfauthor={Your Name},
    pdfsubject={Memory Management in x86},
    pdfkeywords={paging, memory, x86, operating systems}
}

% Code listing styling
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=2
}

\lstset{style=mystyle}

\geometry{margin=2.5cm}
\onehalfspacing

\begin{document}

\chapter{Task 02: Test Paging Activation}

\section{Objective}
The goal of this task is to verify that paging is active by attempting to access unmapped memory. This will help confirm that the paging mechanism is functioning as expected.

\section{Implementation Plan}
\begin{enumerate}
    \item Declare a global variable to serve as a reference for mapped memory.
    \item Create a pointer that points to an address 4MB beyond the global variable. This address should not be mapped since only the first 4MB are initialized.
    \item Attempt to read from the unmapped pointer and observe the behavior.
    \item Temporarily disable paging by modifying the control register (\texttt{cr0}).
    \item Repeat the read operation with paging disabled.
    \item Document the results for both cases (paging enabled and disabled).
\end{enumerate}

\section{Expected Outcome}
\begin{itemize}
    \item With paging enabled:
    \begin{itemize}
        \item Accessing the unmapped pointer should trigger a page fault.
    \end{itemize}
    \item With paging disabled:
    \begin{itemize}
        \item The read operation should succeed, as the memory address will be treated as a physical address.
    \end{itemize}
\end{itemize}

\section{Results}
(To be filled after implementation)

\section{Challenges}
(To be filled after implementation)

\section{Conclusion}
(To be filled after implementation)

\end{document}
